---
title: "Simulate scratching game"
author: "Alban Ott"
date: "15 février 2020"
output:
  rmdformats::readthedown:
    code_folding: hide
    self_contained: true
    thumbnails: false
    lightbox: false
---

```{r}
rm(list=ls())
library(dplyr)
library(tidyr)
library(ggplot2)
theme_set(theme_bw())
```

The cheaper the game is the more iit is played


# Input data
```{r}
#source: https://www.bfmtv.com/loto/les-probabilites-de-gagner-aux-loteries-et-jeux-a-gratter-1460504.html
known_stats = read.table(text="Nom du jeu	Mise	Gain max.	Probabilite gain max.	Probabilite gain	Esperance gain
10 ans gagnants	5	340000	1500000	4.21	-1.4
Astro	2	20000	1125000	3.28	-0.67
Banco	1	1000	750000	4.24	-0.37
Black Jack	2	40000	1500000	4.46	-0.63
Cash	5	500000	6000000	3.83	-1.45
Goal	1	4000	1500000	3.97	-0.35
Jackpot	5	500000	6000000	5.5	-1.4
Maxi Goal	3	40000	1500000	3.83	-0.35
Maxi Mots Croises	5	250000	1500000	3.81	-1.5
Millionnaire	10	1000000	1500000	3.35	-2.65
Mini Mots Croises	2	15000	750000	3.66	-0.68
Mots Croises	3	30000	750000	4.52	-1.46
Mega Mots Croises	10	600000	3000000	2.94	-2.8
Numero Fetiche	1	1000	500000	3.53	-0.37
Pactole	2	200000	4500000	4.26	-0.64
Solitaire	2	25000	1500000	3.44	-0.68
Vegas	3	50000	1000000	3.81	-0.9",
header=TRUE,
sep="\t")

known_stats$Win.Prob = 1/known_stats$Probabilite.gain
known_stats$Prob.Play = known_stats$Mise/sum(known_stats$Mise)
```

# Simulate 3 groups


## Parameters
Decide the balance between the 3 groups, do they all have the same probability to win ?
```{r}
Number_of_players=5000

win_chance_factor=c(Lucky=1,Normal=1,Unlucky=1)
Player_repartition=c(Lucky=33,Normal=33,Unlucky=33)
Avg_number_of_play=5
```

## Usefull derivatives
```{r}
Num_categories_of_player=length(Player_repartition)
Categories_of_player=names(Player_repartition)
Player_repartition = Player_repartition/sum(Player_repartition)
```

## Data simulation

one line per play
```{r}
Observation = data.frame(id.player = 1:Number_of_players)
```

Category of each player
```{r}
Observation = Observation %>% 
  mutate(category = sample(x = Categories_of_player,
                                           size = Number_of_players,
                                           prob = Player_repartition,
                                           replace = TRUE)
)
```

How many time do they play
```{r}
Observation$Play.Num=rnorm(n = Number_of_players, mean = Avg_number_of_play) %>% 
  round()
```


Duplicate each player for each time they play
```{r}
Observation = Observation %>%
  uncount(Play.Num,
          .id="id.game",
          .remove=FALSE) 

```

What game are they playing ?
NB: the cheaper the game is the more iit is played
```{r}
Observation = Observation %>% 
  mutate(Game = sample(x = known_stats$Nom.du.jeu,
                          size = n(), 
                          prob=known_stats$Prob.Play,
                          replace = TRUE)
  )
```

Add probability of winning to this game
```{r}
Observation = left_join(Observation, known_stats[,c("Nom.du.jeu","Win.Prob")],
          by=c("Game" = "Nom.du.jeu")
)
```

Add the additional chance of this category of player
```{r}
tmp = data.frame(category=names(win_chance_factor),win_chance_factor=win_chance_factor)

Observation = left_join(Observation,tmp,
          by="category"
)
```

Adjust the win probability according to the chance of this category of player
```{r}
Observation = Observation %>% 
  mutate(Adj.Win.Prob=Win.Prob*win_chance_factor) %>% 
  mutate(Adj.Win.Prob = if_else(Adj.Win.Prob>1,
                                true=1,
                                false=Adj.Win.Prob))
```


Do they win ?

```{r}
Observation = Observation %>% 
  rowwise() %>% 
  mutate(Win.Loose=sample(x = c("Win","Loose"),
                          size = 1,
                          prob = c(Adj.Win.Prob,1-Adj.Win.Prob)
                          )
         ) %>% 
  ungroup()
```




# Result analysis

## Distribution of players win rate
```{r}
Analysis = Observation %>% 
  group_by(id.player,category) %>% 
  summarize(freq_win=sum(Win.Loose=="Win")/n())

ggplot(Analysis, aes_string("category","freq_win",fill="category"))+
  geom_boxplot()+
  stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show_guide = FALSE)+
  ggtitle("Distribution of players win rate")
```


# Statistical analysis

```{r}
chisq.test(Observation$Win.Loose,Observation$category)
```



